\section{Related Work}

\parhead{Related Surveys.}
Bravo et al.\,\cite{Bravo2018} in their review of intuitive robot programming environments for education categorized robot programming languages into textual, visual, and tangible languages. However, they did not discuss individual language features that facilitate end-user programming, as we do. % The survey gave us the basis to figure out what identifies the various visual, textual and tangible programming languages as shown in figure \ref{fig:featuremodel}.
Biggs et al.\,\cite{Biggs2003} surveyed robot programming systems, in which they have classified the systems into manual programming systems and automatic systems. The manual ones require users to specify missions, while automatic systems control robots based on their interactions with the environment, indicating that such missions are specified on a higher level, for instance, by declaring the mission goals instead of the concrete movements. However, the survey did not discuss language features that enhance robot programming by novice programmers.
Celine Ray et al.\,\cite{CelineRayFrancescoMondadaMemberIEEEandRolandSiegwartFellow2008} in their survey of what people expect from robots realized that elements that appear at personal level include household daily tasks, security, entertainment, and company (child, animal, or elderly care). More than half of them expect the robots providing such services to be in market soon. For someone to get such services from robots, it becomes necessary that mission specification be raised to higher level of expressiveness, which is close to the user domain for easy management of several missions. However, the survey did not cover the available languages, which promote flexible programming of robots by end-user and identify the features required to support novice programmers.
Abdelfetah Hentout et al.\,\cite{Hentout2017} survey development environments for robotics. They identified frameworks for programming robotic system, but not targeting mission specification.
%In ensuring high degree of usability of robotic systems, it is important that the primitives used to specify missions depict the aspects of that user domain \cite{Benyon1996}, while considering the mission behavior to robot capabilities.

% Block programming: Ability to program robots requires enormous effort and time making it hard to deploy them in the community \cite{Weintrop2018}\tb{what kind of work is that?}. New robots are more powerful and flexible, however in order to support robot presence in everyday lives, there is need for quick reprogramming support. Lego mindstroms uses visual blocks to represent basic robot actions which users can organize to produce desired outcomes. There is a challenge of creating meaningful icon for every possible command. Sample tools include;(a)Universal Robot’s tree-based programming tool, in which specification is done  both graphically and and text script, ... (b) Lego mindstorms ...

A survey on DSLs for robotics by Nordmann et al.\,\cite{Nordmann2016a} identified a large number of languages, but surprisingly, none of the languages support mission specification and this makes this work distinct from our study.
%analyzed various issues about modelling languages, with negligible work on mission specification in particular.
Specifically, the survey covered aspects of environmental features and constraints, which are expressed using formalism such as LTL, OWL, and (E)BNF. While scenario definitions are made by using formalisms such as ANTLR grammar, (E)BNF, UML/MOF, LTL, or Ecore. These formalisms are suitable to be used by robotic and software engineers, but not by novice end-users. This gap also motivates our study.
\citet{bacca.ea:2017:teachingrobots} covered a list of mobile robot development platforms for engineering education, covering basic, middle and advanced learners. In their basic learner category, which best fits our end-user category are \aseba, and \edison, which this study also covered. However, for reason ranging from availability of the platforms and end-user facing condition in the inclusion/exclusion criteria, this study could not cover all the development platforms they listed. we provide the most complete list of environments, relying on a systematic search process involving multiple data sources.  %\tb{Swaib, can you check this one? they list a couple more environments, some of which aren't covered in our survey (actually, you have this publication in the repo, as a material for Edison; did you check the environments they listed in addition to ours?)}
% \begin{itemize}
% 	\item 
% 	\item another argument over the existing surveys: we provide the most complete one, relying on a systematic search process
%	\item Labview experiment on programmer productivity: visual syntax enhances programmer productivity\,\cite{WHITLEY.ea:2001:labview}.
% \end{itemize}

\parhead{Beyond Language-Based Mission Specification.}
Gorostiza et al.\,\cite{Gorostiza2011} propose a natural programming environment in which robot skills are accessed verbally to interact with end-users. The environment uses dialog system to extract actions and conditions to create a sequence function chart. The challenge with this approach is, the end-user cannot add new dialogue constructs for new tasks, making the languages inflexible. % to end-user.
Miguel Campusano et al.\,\cite{campusano.ea:2017:live} in their work on ``live robot programming'' have implemented a language that supports live  feedback; this language helps end-users in rapid creation and variation of robot behavior at run-time. This approach however does not provide end-user with domain constructs to simplify the programming effort during mission specification. Doherty et al \cite{Doherty2013}, propose a framework and architecture for automated specification, generation and execution missions for multiple drones, which collaborate with humans. The focus of the study is on how the language can clearly and concisely specify and generate missions, but not on how the language is easy for %the ease of using the language by 
end-users.
%\parhead{Other works}
% Rutle et al. \cite{rutle.ea:2018:commonlang} present a DSL for specifying robotic tasks\tb{not sure how this is related work}
